The results of this paper, as well as areas that were not able to be explored, demonstrate many areas that deserve further research.

\begin{itemize}
    \item A future study could explore different time-of-day pricing scenarios. For example, this study assumed the user took part in Rocky Mountain Power's time-of-day pricing program. However, there is also a traditional program offered that has a flat rate for all times of the day. It may be interesting to explore whether any significant savings can be found using the technologies in this paper when switching from the standard model to the time-of-day mode.
    \item Different locales should be studied to understand the benefits of technologies in different areas. For instance, this study assumed the location as Logan, UT, which has a decent amount of solar radiation. Conducting the same study for somewhere such as Seattle and comparing it to somewhere else such as Phoenix could yield vastly different results that might be worth studying.
    \item This paper took the approach of using Monte Carlo tree search for deciding the battery action at each hour. There are many optimizations that might be made to Monte Carlo tree search that might yield better results. In addition, it might be interesting to try entirely different optimization algorithms. The simulator program is set up to do that if someone in the future chooses to implement such a feature.
    \item It might be beneficial to add more granularity to the battery decisions. This study only allowed 21 possible battery states. However, it might be better to allow for a continuum of states. Such a modification would require different algorithms than Monte Carlo tree search, but might allow for greater savings with no necessary modifications in hardware.
    \item It may be beneficial to explore different energy usage curves. This study assumed an "ideal" curve to be as close to steady as possible. However, it might be even more beneficial to shift loads from on-peak times (such as evenings) to entirely off-peak times, such as the middle of the night or early morning. It would be fairly easy to simulate different curves using the current simulator.
    \item There are other technologies such as wind turbines and heat pumps that are marketed to consumers. Adding these technologies to the system would allow for a more comprehensive look at the state of current technologies.
    \item Some locales allow for "net metering", where excess energy can be fed into the power grid in exchange for energy credits. This simulation assumed that net metering was not permitted. However, the change would be trivial to allow net metering in simulations. This could yield interesting results that may be helpful in exploring areas such as energy policy.
\end{itemize}